---
title: "R Notebook"
output: html_notebook
---


```{r}

#Loading an cleaning data


library(WGCNA)
# The following setting is important, do not omit.
options(stringsAsFactors = FALSE);

workingDir = "C:/Users/cooli/Documents/School/Scriptie";
setwd(workingDir);

data <- readRDS('L6_8000.RDS')
sample <- readRDS('sample_8000.RDS')

all.equal(rownames(data), rownames(sample))

# replace troublesome symbols in colnames (these symbols will mess up in RF)
colnames(data) <- gsub(colnames(data), pattern = "\\[|\\]", replacement = "")
colnames(data) <- gsub(colnames(data), pattern = " ", replacement = "_")


# check for later
mean(colMeans(data[]))


# check if all samples have read counts > 8000
all(rowSums(data) > 8000) # True

# Filter out bacteria with read counts in less than 10% of samples (0 count in more than 90%)
zero_pct <- sapply(data, function(e) mean(e==0))
sum(zero_pct < 0.9) # 59 remain
data <- data[ ,zero_pct < 0.9]

mean(colMeans(data[]))

oral_dat <- data

```



We now have clean bacteria count data in the dataframe "oral_dat"
And patient data in the dataframe "sample"


```{r}


 # Compositional + log transform (spearman correlation)


# function to make data compositional
comp <- function(x) {
  x <- apply(x,1,function(x) (x/sum(x)))
  return(t(x))
}

# clr1: add + 1 to count data for possible missing reads and for maths
# clr1: make data compositional
# clr1: take logarithm
# clr1: minus rowMeans to show relative abundance.
clr1 <- function(x){
  x <- x + 1
  x <- comp(x)
  x <- log(x)
  x <- x - rowMeans(x)
  return(x)
}
oral_comp <- comp(oral_dat)
oral_comp_cor <- cor(oral_comp, method="spearman")

oral_clr1 <- clr1(oral_dat)
oral_clr1_spearman <- cor(oral_clr1, method="spearman")

```


```{r}

library(ggplot2)
library(reshape2)

# Get upper triangle of the correlation matrix
get_upper_tri <- function(cormat){
  cormat[lower.tri(cormat)]<- NA
  return(cormat)
}

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}



```







```{r}
  # Build correlation matrix using SparCC


library(SpiecEasi)

#SparCC is non-deterministic. We run it 10 times and take the average to get more consisten results

oral_sparcc <- sparcc(oral_dat, iter = 20, inner_iter = 10, th = 0.1)
  # oral_sparcc contains 2 matrices, the first is the covariance matrix, the second is the correlation matrix.
  oral_sparcc_cor <- oral_sparcc[[2]]
  
for (i in c(1:9)) {
  oral_sparcc <- sparcc(oral_dat, iter = 20, inner_iter = 10, th = 0.1)
  # oral_sparcc contains 2 matrices, the first is the covariance matrix, the second is the correlation matrix.
  oral_sparcc_cor <- oral_sparcc_cor + oral_sparcc[[2]]
}



oral_sparcc_cor <- oral_sparcc_cor/10

#save(oral_sparcc_cor, file="Oral_sparcc_avgcor.RData")

######################## fix colnames and rownames of sparcc cor matrix
########################


cormat <- oral_sparcc_cor
# Reorder the correlation matrix
cormat <- reorder_cormat(oral_sparcc_cor)

median(cormat)
IQR(cormat)


#colnames(cormat) = colnames(oral_clr1)
#rownames(cormat) = colnames(oral_clr1)
upper_tri <- get_upper_tri(cormat)
# Melt the correlation matrix
melted_cormat <- melt(upper_tri, na.rm = TRUE)
# Create a ggheatmap
ggheatmap <- ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="SparCC\nCorrelation") +
  theme(axis.text = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_blank())
# Print the heatmap
print(ggheatmap)



```

```{r}
  # Build correlation matrix using Compositional


######################## fix colnames and rownames of sparcc cor matrix
########################


cormat <- oral_comp_cor
# Reorder the correlation matrix
cormat <- reorder_cormat(oral_comp_cor)

median(cormat)
IQR(cormat)

colnames(cormat) = colnames(oral_sparcc_cor)
rownames(cormat) = colnames(oral_sparcc_cor)

upper_tri <- get_upper_tri(cormat)
# Melt the correlation matrix
melted_cormat <- melt(upper_tri, na.rm = TRUE)


ggheatmap <- ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Spearman\nCorrelation") +
  theme(axis.text = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_blank())
        
# Print the heatmap
print(ggheatmap)



```

```{r}
cormat <- oral_clr1_spearman
# Reorder the correlation matrix
cormat <- reorder_cormat(oral_clr1_spearman)

median(cormat)
IQR(cormat)

colnames(cormat) = colnames(oral_sparcc_cor)
rownames(cormat) = colnames(oral_sparcc_cor)

upper_tri <- get_upper_tri(cormat)
# Melt the correlation matrix
melted_cormat <- melt(upper_tri, na.rm = TRUE)
# Create a ggheatmap
ggheatmap <- ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Spearman\nCorrelation") +
  theme(axis.text = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_blank())
        
# Print the heatmap
print(ggheatmap)
```


###############################################
# Correlation matrices have been constructed
###############################################


```{r}
nSamples = 174
nGenes = 59
nEdges = nGenes * (nGenes-1) / 2

gamma = log(nEdges, base=(sqrt(nSamples)))
print(gamma)


# A gamma of 2.89 indicates that any soft power scaling of over 2.89 is okay.
# Power should not be a lot higher than gamma.
# 

```






```{r}

##  Looking at Scale independence and mean connectivity of clr1 correlation matrix
## Results are quite poor, A power of 4 seems most appropriate.
## picking a power of 3 based on the gamma calculated above also remains as an option.

sim_matrix <- abs(oral_clr1_spearman)


powers = c(c(1:10), seq(from = 12, to=20, by=2))
sft = pickSoftThreshold.fromSimilarity(sim_matrix, powerVector = powers, verbose = 5)


# Plot the results:
sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
     main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     labels=powers,cex=cex1,col="red");
# this line corresponds to using an R^2 cut-off of h
abline(h=0.9,col="red")
# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
     xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
     main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")




```


```{r}

##########################################################
##########################################################
##########################################################
## TOM construction
## 
##########################################################
##########################################################
##########################################################

oral_similarity_clr1 <- abs(oral_clr1_spearman)

## Picking soft power of 3 based on calculation above
softPower = 3
oral_adjacency_clr1 <- adjacency.fromSimilarity(oral_similarity_clr1, power = softPower)
oral_TOM_clr1 = TOMsimilarity(oral_adjacency_clr1, TOMType = "unsigned")
oral_dissTOM_clr1 = 1 - oral_TOM_clr1

# Call the hierarchical clustering function
oral_geneTree_clr1 = hclust(as.dist(oral_dissTOM_clr1), method = "average");
# Plot the resulting clustering tree (dendrogram)
sizeGrWindow(12,9)
plot(oral_geneTree_clr1, xlab="", sub="", main = "Gene clustering on TOM-based dissimilarity",
     labels = FALSE, hang = 0.04);


# Setting module size is important and has great impact on the modules formed.
# We pick a module size of 3, keeping in mind the relatively low amount of bacteria (24)
minModuleSize = 3;
# Module identification using dynamic tree cut:
oral_dynamicMods_clr1 = cutreeDynamic(dendro = oral_geneTree_clr1, distM = oral_dissTOM_clr1,
                            deepSplit = 2, pamRespectsDendro = FALSE,
                            minClusterSize = minModuleSize);
table(oral_dynamicMods_clr1)





# Convert numeric lables into colors
oral_dynamicColors_clr1 = labels2colors(oral_dynamicMods_clr1)
table(oral_dynamicColors_clr1)
# Plot the dendrogram and colors underneath
sizeGrWindow(8,6)
plotDendroAndColors(oral_geneTree_clr1, oral_dynamicColors_clr1, "Dynamic Tree Cut",
                    dendroLabels = FALSE, hang = 0.03,
                    addGuide = TRUE, guideHang = 0.05,
                    main = "Gene dendrogram and module colors, CLR1")







```


```{r}

datExpr = oral_clr1

# Calculate eigengenes


oral_MEList_clr1 = moduleEigengenes(datExpr, colors = oral_dynamicColors_clr1)
oral_MEs_clr1 = oral_MEList_clr1$eigengenes
# Calculate dissimilarity of module eigengenes
oral_MEDiss_clr1 = 1-cor(oral_MEs_clr1);
# Cluster module eigengenes
oral_METree_clr1 = hclust(as.dist(oral_MEDiss_clr1), method = "average");
# Plot the result
sizeGrWindow(7, 6)
plot(oral_METree_clr1, main = "Clustering of module eigengenes, based of clr1 tranformed data",
     xlab = "", sub = "")

####
# Plot shows that no merging is necessarry
###
oral_moduleColors_clr1 <- oral_dynamicColors_clr1

```







```{r}

library(igraph)

Probes=colnames(oral_dat)

dimnames(oral_TOM_clr1) = list(Probes, Probes)


oral_net_clr1 <- graph_from_adjacency_matrix(oral_TOM_clr1, mode = "undirected", weighted = TRUE, diag=F)

# Calculate network density:
sum(E(oral_net_clr1)$weight/(gsize(oral_net_clr1)))


oral_net_clr1 <- set_vertex_attr(oral_net_clr1, "color", value = oral_moduleColors_clr1)
plot(oral_net_clr1)


# calculate node strength: the sum of all edge weights of a node.
# stronger nodes are better connected and persumably of more biological importance.
V(oral_net_clr1)$strength <- strength(oral_net_clr1, mode="all")

plot(oral_net_clr1, 
     vertex.size= V(oral_net_clr1)$strength * 30)

# Delete all edges with a value under 0.05 in the TOM, only the strongest edges remain
oral_trimmed_clr1 <- delete.edges(oral_net_clr1, which(E(oral_net_clr1)$weight <0.05))


## Contruct the finished network 

plot(oral_trimmed_clr1, 
     vertex.size= V(oral_net_clr1)$strength * 10,
     vertex.label.color="black",
     vertex.color = adjustcolor(V(oral_net_clr1)$color, alpha.f=0.6), # make nodes slightly opaque to improve readability
     frame.color=NA, #trying to remove the black frame surrounding the vertices (unsuccesfully)
     main="Network construction based on clr + 1 transformed count data",
     sub="edges>0.05 in the TOM are shown. Node size indicates strength of node")


plot(oral_trimmed_clr1, 
     vertex.size= V(oral_net_clr1)$strength * 10,
     vertex.label="",
     vertex.label.color="black",
     vertex.color = adjustcolor(V(oral_net_clr1)$color, alpha.f=0.6), # make nodes slightly opaque to improve readability
     frame.color=NA, #trying to remove the black frame surrounding the vertices (unsuccesfully)
     main="Network construction based on clr + 1 transformed count data",
     sub="edges>0.05 in the TOM are shown. Node size indicates strength of node")




```


```{r}

## Looking at scale independence and Mean connectivity of Sparcc correlation matrix
## Results aren't great
## A power of 3 seems most appropriate

sim_matrix <- abs(oral_sparcc_cor)


powers = c(c(1:10), seq(from = 12, to=20, by=2))
sft = pickSoftThreshold.fromSimilarity(sim_matrix, powerVector = powers, verbose = 5)
# Plot the results:
sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
     main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     labels=powers,cex=cex1,col="red");
# this line corresponds to using an R^2 cut-off of h
abline(h=0.9,col="red")
# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
     xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
     main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")



```


```{r}


oral_similarity_sparcc <- abs(oral_sparcc_cor)

## Picking soft power of 4 To keep it identical to the CLR1 power
softPower = 3
oral_adjacency_sparcc <- adjacency.fromSimilarity(oral_similarity_sparcc, power = softPower)
oral_TOM_sparcc = TOMsimilarity(oral_adjacency_sparcc, TOMType = "unsigned")
oral_dissTOM_sparcc = 1 - oral_TOM_sparcc

# Call the hierarchical clustering function
oral_geneTree_sparcc = hclust(as.dist(oral_dissTOM_sparcc), method = "average");
# Plot the resulting clustering tree (dendrogram)
sizeGrWindow(12,9)
plot(oral_geneTree_sparcc, xlab="", sub="", main = "Gene clustering on TOM-based dissimilarity",
     labels = FALSE, hang = 0.04);




# Setting module size is important and has great impact on the modules formed.
# We pick a module size of 3, keeping in mind the relatively low amount of bacteria (24)
minModuleSize = 3;
# Module identification using dynamic tree cut:
oral_dynamicMods_sparcc = cutreeDynamic(dendro = oral_geneTree_sparcc, distM = oral_dissTOM_sparcc,
                                 deepSplit = 2, pamRespectsDendro = FALSE,
                                 minClusterSize = minModuleSize);
table(oral_dynamicMods_sparcc)



# Convert numeric lables into colors
oral_dynamicColors_sparcc = labels2colors(oral_dynamicMods_sparcc)
table(oral_dynamicColors_sparcc)
# Plot the dendrogram and colors underneath
sizeGrWindow(8,6)
plotDendroAndColors(oral_geneTree_sparcc, oral_dynamicColors_sparcc, "Dynamic Tree Cut",
                    dendroLabels = FALSE, hang = 0.03,
                    addGuide = TRUE, guideHang = 0.05,
                    main = "Gene dendrogram and module colors, SparCC")




```


```{r}

datExpr = oral_dat

# Calculate eigengenes

# Merging might be problematic due to the SparCC algorithm.
# Correlation matrix from SparCC, Module Eigengenes calculation does not benefit from SparCC computations.
oral_MEList_sparcc = moduleEigengenes(datExpr, colors = oral_dynamicColors_sparcc)
oral_MEs_sparcc = oral_MEList_sparcc$eigengenes
# Calculate dissimilarity of module eigengenes
oral_MEDiss_sparcc = 1-cor(oral_MEs_sparcc);
# Cluster module eigengenes
oral_METree_sparcc = hclust(as.dist(oral_MEDiss_sparcc), method = "average");
# Plot the result
sizeGrWindow(7, 6)
plot(oral_METree_sparcc, main = "Clustering of module eigengenes, based of clr1 tranformed data",
     xlab = "", sub = "")

####
# Plot shows that no merging is necessarry
###

# naming for comparison with clr1 results later
oral_moduleColors_sparcc <- oral_dynamicColors_sparcc
  






```


```{r}

##########################################################
##########################################################
##########################################################
## Basic Network construction
## 
##########################################################
##########################################################
##########################################################

library(igraph)

Probes=colnames(oral_dat)

dimnames(oral_TOM_sparcc) = list(Probes, Probes)


oral_net_sparcc <- graph_from_adjacency_matrix(oral_TOM_sparcc, mode = "undirected", weighted = TRUE, diag=F)

# Calculate network density:
sum(E(oral_net_sparcc)$weight/(gsize(oral_net_sparcc)))


oral_net_sparcc <- set_vertex_attr(oral_net_sparcc, "color", value = oral_moduleColors_sparcc)
plot(oral_net_sparcc)


# calculate node strength: the sum of all edge weights of a node.
# stronger nodes are better connected and persumably of more biological importance.
V(oral_net_sparcc)$strength <- strength(oral_net_sparcc, mode="all")

plot(oral_net_sparcc, 
     vertex.size= V(oral_net_sparcc)$strength * 90)

# Delete all edges with a value under 0.01 in the TOM, only the strongest edges remain
oral_trimmed_sparcc <- delete.edges(oral_net_sparcc, which(E(oral_net_sparcc)$weight <0.05))


## Contruct the finished network 

plot(oral_trimmed_sparcc, 
     vertex.size= V(oral_net_sparcc)$strength * 30,
     vertex.label.color="black",
     vertex.color = adjustcolor(V(oral_net_sparcc)$color, alpha.f=0.6), # make nodes slightly opaque to improve readability
     frame.color=NA, #trying to remove the black frame surrounding the vertices (unsuccesfully)
     main="Network construction of Oral bacteria based on SparCC correlation matrix",
     sub="edges>0.02 in the TOM are shown. Node size indicates strength of node")

plot(oral_trimmed_sparcc, 
     vertex.label ="",
     vertex.size= V(oral_net_sparcc)$strength * 30,
     vertex.label.color="black",
     vertex.color = adjustcolor(V(oral_net_sparcc)$color, alpha.f=0.6), # make nodes slightly opaque to improve readability
     frame.color=NA, #trying to remove the black frame surrounding the vertices (unsuccesfully)
     main="Network construction of Oral bacteria based on SparCC correlation matrix",
     sub="edges>0.02 in the TOM are shown. Node size indicates strength of node")



```


########
####### CONSENSuS ANALYSIS



```{r}
# Isolate the module labels in the order they appear in ordered module eigengenes
oral_dynamicMods_clr1 = substring(names(oral_MEs_clr1), 3)
oral_dynamicMods_sparcc = substring(names(oral_MEs_sparcc), 3)
# Convert the numeric module labels to color labels
oral_clr1_Modules = oral_dynamicMods_clr1#
oral_sparcc_Modules = oral_dynamicMods_sparcc#
# Numbers of clr1 and sparcc modules
oral_nClr1Mods = length(oral_clr1_Modules)
oral_nSparccMods = length(oral_sparcc_Modules)
# Initialize tables of p-values and of the corresponding counts
pTable = matrix(0, nrow = oral_nClr1Mods, ncol = oral_nSparccMods);
CountTbl = matrix(0, nrow = oral_nClr1Mods, ncol = oral_nSparccMods);
# Execute all pairwaise comparisons
for (fmod in 1:oral_nClr1Mods)
  for (cmod in 1:oral_nSparccMods)
  {
    oral_clr1_Members = (oral_moduleColors_clr1 == oral_clr1_Modules[fmod]);
    oral_sparcc_Members = (oral_moduleColors_sparcc == oral_sparcc_Modules[cmod]);
    pTable[fmod, cmod] = -log10(fisher.test(oral_clr1_Members, oral_sparcc_Members, alternative = "greater")$p.value);
    CountTbl[fmod, cmod] = sum(oral_moduleColors_clr1 == oral_clr1_Modules[fmod] & oral_moduleColors_sparcc ==
        oral_sparcc_Modules[cmod])
}

```


```{r}
# Truncate p values smaller than 10^{-50} to 10^{-50}
pTable[is.infinite(pTable)] = 1.3*max(pTable[is.finite(pTable)]);
pTable[pTable>50 ] = 50 ;
# Marginal counts (really module sizes)
oral_clr1_ModTotals = apply(CountTbl, 1, sum)
oral_sparcc_ModTotals = apply(CountTbl, 2, sum)
# Actual plotting
sizeGrWindow(10,7 );
#pdf(file = "Plots/FecalModules.pdf", wi = 10, he = 7);
par(mfrow=c(1,1));
par(cex = 1.0);
par(mar=c(8, 10.4, 2.7, 1)+0.3);
# Use function labeledHeatmap to produce the color-coded table with all the trimmings

labeledHeatmap(Matrix = pTable,
  xLabels = paste(" ", oral_sparcc_Modules),
  yLabels = paste(" ", oral_clr1_Modules),
  colorLabels = TRUE,
  xSymbols = paste("SparCC ", oral_sparcc_Modules, ": ", oral_sparcc_ModTotals, sep=""),
  ySymbols = paste("CLR1 ", oral_clr1_Modules, ": ", oral_clr1_ModTotals, sep=""),
  textMatrix = CountTbl,
  colors = greenWhiteRed(100)[50:100],
  cex.text = 1.0, cex.lab = 1.0, setStdMargins = FALSE)


```






```{r}

# relative abundance barplot of bacteria and module colors


mean_counts <- colMeans(oral_dat)
mean_counts_comp <- colMeans(oral_comp)

#barplot(mean_counts,main="Mean bacteria Counts, bar color = CLR1 module color",ylab="Counts (logarithmic scale!)",xlab="",las=2, log="y", col=oral_moduleColors_clr1)

barplot(mean_counts_comp,main="Relative bacteria Abundance, bar color = CLR1 module color",ylab="Counts (logarithmic scale!)",xlab="",las=2, log="y", col=oral_moduleColors_clr1)


```



```{r}

#barplot(mean_counts,main="Mean bacteria Counts, bar color = SparCC module color",ylab="Counts (logarithmic scale!)",xlab="",las=2, log="y", col=oral_moduleColors_sparcc)

barplot(mean_counts_comp,main="Relative bacteria Abundance, bar color = SparCC module color",ylab="Counts (logarithmic scale!)",xlab="",las=2, log="y", col=oral_moduleColors_sparcc)

```












###############################################
# We will Now look at a couple interesting modules.
# We are interested if modules found by these techniques
# Make sense on a biological level
###############################################








CLR1 blue and brown modules and SParCC brown and turquoise modules will be show in detail




```{r}
#######################################################################
# Select brown module, visualize network using Igraph
#######################################################################

module="brown"

probes = colnames(oral_dat)

#sparCC
inModule = is.finite(match(oral_moduleColors_sparcc, module));
modProbes= probes[inModule]
modTOM = oral_TOM_sparcc[inModule,inModule]

dimnames(modTOM) = list(modProbes, modProbes)

brown_net_sparcc <- graph_from_adjacency_matrix(modTOM, mode = "undirected", weighted = TRUE, diag=F)
sum(E(brown_net_sparcc)$weight/(gsize(brown_net_sparcc)))

# Size of a node is the sum of all its weighted edges
V(brown_net_sparcc)$size <- strength(brown_net_sparcc, mode="all") * 100

#vertex.size= V(oral_net_sparcc)$strength * 30

# REmove edges with low weights
brown_net_sparcc <- delete.edges(brown_net_sparcc, which(E(brown_net_sparcc)$weight <0.02))

plot(brown_net_sparcc, 
     vertex.label.color="black",
     vertex.color = adjustcolor(module, alpha.f=0.6)) # make nodes slightly opaque to improve readability)



# REmove edges with low weights
brown_net_sparcc <- delete.edges(brown_net_sparcc, which(E(brown_net_sparcc)$weight <0.05))

plot(brown_net_sparcc, 
     vertex.label.color="black",
     vertex.color = adjustcolor(module, alpha.f=0.6)) # make nodes slightly opaque to improve readability)


```









```{r}
#######################################################################
# Select turquoise module, visualize network using Igraph
#######################################################################

module="turquoise"

probes = colnames(oral_dat)

#SparCC
inModule = is.finite(match(oral_moduleColors_sparcc, module));
modProbes= probes[inModule]
modTOM = oral_TOM_sparcc[inModule,inModule]

dimnames(modTOM) = list(modProbes, modProbes)

net_sparcc <- graph_from_adjacency_matrix(modTOM, mode = "undirected", weighted = TRUE, diag=F)
sum(E(net_sparcc)$weight/(gsize(net_sparcc)))

# Size of a node is the sum of all its weighted edges
V(net_sparcc)$size <- strength(net_sparcc, mode="all") * 50



# REmove edges with low weights
net_sparcc <- delete.edges(net_sparcc, which(E(net_sparcc)$weight <0.02))

plot(net_sparcc, 
     vertex.label.color="black",
     vertex.color = adjustcolor("turquoise", alpha.f=0.6)) # make nodes slightly opaque to improve readability)



# REmove edges with low weights
net_sparcc <- delete.edges(net_sparcc, which(E(net_sparcc)$weight <0.05))

plot(net_sparcc, 
     vertex.label.color="black",
     vertex.color = adjustcolor("turquoise", alpha.f=0.6)) # make nodes slightly opaque to improve readability)


```




```{r}

#######################################################################
# Select blue module, visualize network using Igraph
#######################################################################

module="blue"

probes = colnames(oral_dat)

#CLR1
inModule = is.finite(match(oral_moduleColors_clr1, module));
modProbes= probes[inModule]
modTOM = oral_TOM_clr1[inModule,inModule]

dimnames(modTOM) = list(modProbes, modProbes)

blue_net_clr1 <- graph_from_adjacency_matrix(modTOM, mode = "undirected", weighted = TRUE, diag=F)
sum(E(blue_net_clr1)$weight/(gsize(blue_net_clr1)))


# Size of a node is the sum of all its weighted edges
V(blue_net_clr1)$size <- strength(blue_net_clr1, mode="all") * 20


# REmove edges with low weights
blue_net_clr1 <- delete.edges(blue_net_clr1, which(E(blue_net_clr1)$weight <0.02))

plot(blue_net_clr1, 
     vertex.label.color="black",
     vertex.color = adjustcolor("blue", alpha.f=0.5)) # make nodes slightly opaque to improve readability)



# REmove edges with low weights
blue_net_clr1 <- delete.edges(blue_net_clr1, which(E(blue_net_clr1)$weight <0.05))

plot(blue_net_clr1, 
     vertex.label.color="black",
     vertex.color = adjustcolor("blue", alpha.f=0.5)) # make nodes slightly opaque to improve readability)










```









```{r}

#######################################################################
# Select brown module, visualize network using Igraph
#######################################################################

module="brown"

probes = colnames(oral_dat)

#CLR1
inModule = is.finite(match(oral_moduleColors_clr1, module));
modProbes= probes[inModule]
modTOM = oral_TOM_clr1[inModule,inModule]

dimnames(modTOM) = list(modProbes, modProbes)

net_clr1 <- graph_from_adjacency_matrix(modTOM, mode = "undirected", weighted = TRUE, diag=F)
sum(E(net_clr1)$weight/(gsize(net_clr1)))

# Size of a node is the sum of all its weighted edges
V(net_clr1)$size <- strength(net_clr1, mode="all") * 20


# REmove edges with low weights
net_clr1 <- delete.edges(net_clr1, which(E(net_clr1)$weight <0.02))

plot(net_clr1, 
     vertex.label.color="black",
     vertex.color = adjustcolor("brown", alpha.f=0.6)) # make nodes slightly opaque to improve readability)



# REmove edges with low weights
net_clr1 <- delete.edges(net_clr1, which(E(net_clr1)$weight <0.05))

plot(net_clr1,
     vertex.label.color="black",
     vertex.color = adjustcolor("brown", alpha.f=0.6)) # make nodes slightly opaque to improve readability)












```







